Stable Hot Spot Analysis (Draft)

### 2017-06-15 paper-main.tex
using the auto-generated images
updated images

\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{SoH up for focal size}
    \includegraphics[width=\linewidth]{images/whiskerPlot/fUp}
    \label{fig:fUp}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{SoH down for focal size}
    \includegraphics[width=\linewidth]{images/whiskerPlot/fDown}
    \label{fig:fDown}
  \end{subfigure}
  \caption{SoH for focal size}
  \label{fig:SoHFocal}
\end{figure}

@@

\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{SoH up for weight size}
    \includegraphics[width=\linewidth]{images/whiskerPlot/wUp}
    \label{fig:wUp}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{SoH down for weight size}
    \includegraphics[width=\linewidth]{images/whiskerPlot/wDown}
    \label{fig:wDown}
  \end{subfigure}
  \caption{SoH for weight size}
  \label{fig:SoHWeight}
\end{figure}
%
% Zoom
%	G* alwas better than Focal G* for upward and downward property
%	Focal G* has different focal sizes because zoom is compared
%	At zoom level 4 G* increase much more than Focal G*
%
%	Conclusion: G* is better than Focal G* in the zoom dimension, but the focal size is fixed. The zoom dimension has the least 
%	influence on the value
\subsection{Impact of Aggregation level}
Finally, we isolate the impact of the different aggregation levels on the stability of the hot spot analysis. We fix the aggregation and use it as x-axis. This allows us to examine the impact the resolution of a data set has on the results and allow us indirectly to reduce the computational effort on future computations by using the maximal aggregation as useful.
The results can seen in figure ~\ref{fig:SoHZoom} and ~\ref{fig:DownwardZoom}.
First, we can see that for the zoom level, in contrast to previous results, the standard $G^*$ seems to be more stable.

@@

\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{SoH up for focal size}
    \includegraphics[width=\linewidth]{images/whiskerPlot/zUp}
    \label{fig:zUp}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{SoH down for focal size}
    \includegraphics[width=\linewidth]{images/whiskerPlot/zDown}
    \label{fig:zDown}
  \end{subfigure}
  \caption{SoH for focal size}
  \label{fig:SoHZoom}
\end{figure}

@@

>>>>

\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{SoH up for focal size}
    \includegraphics[width=\linewidth]{images/gen-focal-1}
    \label{fig:fUp}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{SoH down for focal size}
    \includegraphics[width=\linewidth]{images/gen-focal-2}
    \label{fig:fDown}
  \end{subfigure}
  \caption{SoH for focal matrix size}
  \label{fig:SoHFocal}
\end{figure}

@@

\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{SoH up for weight size}
    \includegraphics[width=\linewidth]{images/gen-weight-1}
    \label{fig:wUp}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{SoH down for weight size}
    \includegraphics[width=\linewidth]{images/gen-weight-2}
    \label{fig:wDown}
  \end{subfigure}
  \caption{SoH for weight size}
  \label{fig:SoHWeight}
\end{figure}
%
% Zoom
%	G* alwas better than Focal G* for upward and downward property
%	Focal G* has different focal sizes because zoom is compared
%	At zoom level 4 G* increase much more than Focal G*
%
%	Conclusion: G* is better than Focal G* in the zoom dimension, but the focal size is fixed. The zoom dimension has the least 
%	influence on the value
\subsection{Impact of Aggregation level}
Finally, we isolate the impact of the different aggregation levels on the stability of the hot spot analysis. We fix the aggregation and use it as x-axis. This allows us to examine the impact the resolution of a data set has on the results and allow us indirectly to reduce the computational effort on future computations by using the maximal aggregation as useful.
The results can seen in figure ~\ref{fig:SoHZoom} and ~\ref{fig:DownwardZoom}.
First, we can see that for the zoom level, in contrast to previous results, the standard $G^*$ seems to be more stable.

@@

\begin{figure}[htp]
  \begin{subfigure}{\linewidth}
    \caption{SoH up for focal size}
    \includegraphics[width=\linewidth]{images/gen-aggregation-1}
    \label{fig:zUp}
  \end{subfigure}
  \hspace{1em}
  \begin{subfigure}{\linewidth}
    \caption{SoH down for focal size}
    \includegraphics[width=\linewidth]{images/gen-aggregation-2}
    \label{fig:zDown}
  \end{subfigure}
  \caption{SoH for focal size}
  \label{fig:SoHZoom}
\end{figure}

@@

\begin{figure*}[htp]
  \centering
  \begin{tabular}{cccccccc}
    \multicolumn{8}{l}{Multiple weight matrix sizes} \\
    \hline
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-1}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-2}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-3}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-4}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-5}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-6}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-7}&
    \includegraphics[width=4.6em]{images/gen-blur-wmatrices-8}
  \end{tabular}
  \begin{tabular}{cccccccc}
    \multicolumn{8}{l}{G* Multiple weight matrix sizes} \\
    \hline
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-1}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-2}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-3}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-4}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-5}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-6}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-7}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-gstar-8}
  \end{tabular}
  \begin{tabular}{cccccccc}
    \multicolumn{8}{l}{Focal G* Multipleweight matrix sizes} \\
    \hline
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-1}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-2}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-3}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-4}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-5}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-6}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-7}&
    \includegraphics[width=4.6em]{images/gen-raw-zoom-focalgstar-8}
  \end{tabular}
